---
title: "Hypopo"
subtitle: "Creating presentations with Quarto! {{< iconify simple-icons:quarto >}}"
author: "Ruben C. Kubina"
format: 
  revealjs:
    logo: images/Logo-INRAE_Transparent.png
    footer: "Ruben C. Kubina - 11.07.2024"
    theme: theme.scss
    slide-number: true
    controls: true
    output-file: index.html
    chalkboard: true
    code-line-numbers: false
    mermaid:
      theme: neutral
lightbox: auto
self-contained: false
embed-resources: false
---

## What is Quarto {{< iconify wpf:ask-question >}}
<hr>
<!-- <hr> is a horizontal line which I put under the headings of the slides,
the definition (color, size) is in theme.scss -->

<!-- Here I use inline css to style the output: change color, text to italic, 
center and add a margin under the class -->
:::{style="color: #006264; font-style: italic; text-align: center;margin-bottom: 10px;"}
"Quarto is an open-source scientific and technical publishing system."
:::

<hr>

<!--  Here I use a pandoc class with css to decrease the font size and make the list incremental -->
:::{style="font-size: 30px;" .incremental}

  * Create presentations, websites, blogs, reports and more!
    * reproducible and the option for automatically generating
  
  * Include your {{< iconify devicon:r >}} or Python {{< iconify logos:python >}} code for plots or tables
  
  * Share interactive content with your coworkers (or the world!)
    * Publish with GitHub Pages or other services

:::

<!-- For a better overview I include all the other slides from single quarto files
That makes the document easier to read and it doesn't get too long! -->

{{< include chapters/create_presentation.qmd >}}

{{< include chapters/styling.qmd >}}

{{< include chapters/github_pages.qmd >}}

<!--  This is a title page with a new layout. In this case I added the ae background
and centered the subtitle -->
---

##  {#further-ressources data-menu-title="What else?" background-image="images/ae_light.png"}

<div class="page-center">
<div class="custom-subtitle"> What else? {{< iconify line-md:compass-loop >}}  </div>
</div>

---


## Using leaflet
<hr>

```{r}
#| echo: true
#| message: false
#| warning: false
#| out-width: "100%"
#| output-location: column
library(leaflet)
library(leafem)

leaflet() |>
  addProviderTiles(providers$CartoDB.Positron) |>
  addPopups(
    lat = 45.77864201354321,
    lng = 4.875703855300546,
    "Where we are!",
    options = popupOptions(closeButton = FALSE)
  ) |>
  addHomeButton(
    position = "topright",
    add = T,
    ext = c(4.875703855300546, 45.77864201354321),
    group = "Back to INRAE"
  ) |>
  addMarkers(
    lat = 45.77864201354321,
    lng = 4.875703855300546,
    popup = "Where we are!"
  ) |>
  addPopups(
    lat = 48.00152622812801,
    lng = 7.842766370914802,
    "Where I come from!",
    options = popupOptions(closeButton = FALSE)
  ) |>
  addMarkers(
    lat = 48.00152622812801,
    lng = 7.842766370914802,
    popup = "Where I come from!"
  ) |>
  setView(
    lat = 47.15736580850752,
    lng = 6.109927426870963,
    zoom = 7
  )
```

## Using plotly
<hr>

```{r}
library(plotly)
library(ggplot2)

df <- readRDS("images/goodFit_Loire.RDS")[[1]] |>
  filter(code_bss == "03276X0009/P")

plot <- ggplot() +
  geom_line(data = df, aes(x = dttm, y = value, color = name)) +
  scale_color_manual(values = c("J2000" = "blue", "Ref. Piezometer" = "red"), name = "") +
  theme_minimal() +
  labs(x = "Date", y = "SPLI (-)") +
  theme(legend.position = "bottom") 

ggplotly(plot, dynamicTicks = T) |>
  layout(legend = list(x = 0.8, y = 0.9))
```


## Further Ressources
<hr>
<!--  To embed some links use [TextToDisplay](URL) -->
* [The official Quarto documentation](https://quarto.org/docs/presentations/)

* [R-Studio conference 2022](https://rstudio-conf-2022.github.io/get-started-quarto/materials/05-presentations.html#/auto-animate-1)

* [Sam Csik - Styling Quarto websites](https://ucsb-meds.github.io/customizing-quarto-websites/#/title-slide) 

* [The GitHub repository of this presentation](https://github.com/Carluna/hypopo-quarto)

There's much more to discover: extensions, animations, transitions, tabsets, scrolling, ...


---

##  {#questions data-menu-title="Any questions?" background-image="images/ae_light.png"}

<div class="page-center">
<div class="custom-subtitle"> Thanks for your attention! Questions?  </div>
</div>


